---
output: github_document
---

<!-- badges: start -->
[![R-CMD-check](https://github.com/vohai611/gsovn/workflows/R-CMD-check/badge.svg)](https://github.com/vohai611/gsovn/actions)
<!-- badges: end -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```



The goal of gsovn is to scrape dataset from [gso.gov.vn](https://gso.gov.vn) (Vietnam General statistic organization)

## Installation

You can install the development version of gsovn from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("vohai611/gsovn")
```
## TODO

  1. Add option to download csv

  2. use `{{crul}}` to send asynch request in the case download multiple dataset

## Example

You can check what dataset is now on gso.gov.vn

```{r example}
library(gsovn)
df = gso_avail()
head(df)
```

To get the data set you want, use `gso_read(url)`.

```{r}
df$link[2] |> gso_read()
```

This function call `rvest::html_table()` to parse html to tibble, therefore the result might be slow. I will add the option to download csv file in the future

